---
title: "Hw6"
output: github_document
---

```{r}
library(tidyverse)
library(viridis)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


##Problem 1

```{r}
bwt_df <- read_csv("birthweight.csv", col_types = "fnnnnnfnfnnnfnnnnnnn")
summary(bwt_df)
sum(is.na(bwt_df))
```

The smoke_fit model attempts to use babysex mrace and frace as citnroling factors to determine relationship between smoked and bwt. 
```{r}
smoke_fit <- lm(bwt ~ babysex + mrace + frace + smoken, data = bwt_df)
broom::glance(smoke_fit)
broom::tidy(smoke_fit)


bwt_df %>% 
  add_predictions(smoke_fit) %>% 
  add_residuals(smoke_fit) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red")
```
Comparing models,
```{r}
length_fit <- lm(bwt ~ blength + gaweeks, data = bwt_df)
head_fit <- lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex +bhead*blength*babysex, data = bwt_df)

cv_df <- 
  crossv_mc(bwt_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
  smoke_fit  = map(train, ~lm(bwt ~ babysex + mrace + frace + smoken, data = .x)),
    length_fit = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    head_fit  = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex +bhead*blength*babysex, data = .x))) %>% 
  mutate(
    rmse_smoke = map2_dbl(smoke_fit, test, ~rmse(model = .x, data = .y)),
    rmse_length= map2_dbl(length_fit, test, ~rmse(model = .x, data = .y)),
    rmse_head = map2_dbl(head_fit, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

The model using head circumference, length, sex, and all interactions (including the three-way interaction) between these predictors has the lowest rmse, and would be the most appropriate model. 



##Problem 2
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
Bootstrap
```{r}

weather_boot <- 
weather_df %>% 
  bootstrap(5000) %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax~tmin, data = .x)),
    results = map(.x = models, broom::tidy),
    r_square = map(.x = models, broom::glance)
  ) %>% 
  select(strap, results, r_square) %>% 
  unnest(results, r_square) %>% 
  select(strap, term, estimate, r.squared) %>% 
  pivot_wider(
   names_from = term,
   values_from = estimate
  ) %>% 
  janitor::clean_names() %>% 
  mutate(
    log_est = log(intercept*tmin)
  ) %>% 
  select(-intercept, -tmin)
```

Distributions
```{r}
r_sq_plot <- 
  weather_boot %>% 
  ggplot(aes(x = r_squared)) +
  geom_density()

r_sq_plot


log_est_plot <- 
  weather_boot %>% 
  ggplot(aes(x = log_est)) +
  geom_density()

log_est_plot

```

95%CI

```{r}
weather_boot %>% 
  pivot_longer(
    cols = c(r_squared,log_est),
    names_to = "measures", 
    values_to = "value"
  ) %>% 
  group_by(measures) %>% 
  summarize(
    ci_lower = quantile(value, 0.025),
    ci_upper = quantile(value, 0.975)) %>% 
  knitr::kable()
```


